ACNP 2024 MS ANXIETY

### 2024-08-13 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
playing with promis graphs

# Reshape the data from wide to long format
df_for_promis_plot_mental_vs_physical_healthy <- df_people_with_promis_data_scores_added_unique %>%
  group_by(EMPI) %>%
  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
  dplyr::select(EMPI,
                anxiety_dose,
                physical_health_score,
                mental_health_score) %>%
  gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  group_by(anxiety_dose, health_variable) %>%
  summarise(mean_promis_score = mean(PROMIS_Score , na.rm = TRUE)) %>%
  ungroup()

@@

# Create the ggplot
promis_with_post_op_mental_vs_physical <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, color = health_variable)) +
  geom_line(size = 1.2) +
  scale_x_continuous(breaks = c(0, 1, 2)) +
  scale_y_continuous(limits = c(0, 7)) +
  theme(
       # plot.title = element_text(size=16, hjust = 0.55),
      #  axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
      #  axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
      #  legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white")) +
  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
       title = "PROMIS Scores by Anxiety Dose") +
#  scale_color_brewer(palette = "Set3") 
  scale_color_manual(values = custom_colors_simple)
promis_with_post_op_mental_vs_physical

# Create the ggplot -> bar
promis_with_post_op_mental_vs_physical_bar <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, fill = health_variable)) +
  geom_bar(stat = "identity", position = position_dodge()) +  
  scale_x_continuous(breaks = c(0, 1, 2)) +
  scale_y_continuous(limits = c(0, 7)) +

  theme_minimal() +
  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
       title = "PROMIS Scores by Anxiety Dose") +
  scale_fill_manual(values = custom_colors)

>>>>

# Reshape the data from wide to long format
df_for_promis_plot_mental_vs_physical_healthy <- df_people_with_promis_data_scores_added_unique %>%
  group_by(EMPI) %>%
  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
  dplyr::select(EMPI,
                anxiety_dose,
                physical_health_score,
                mental_health_score) %>%
  gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  group_by(anxiety_dose, health_variable) %>%
  summarise(mean_promis_score = mean(PROMIS_Score , na.rm = TRUE),
            sd_promis_score = sd(PROMIS_Score, na.rm = TRUE),
            sem_promis_score = sd(PROMIS_Score, na.rm = TRUE) / sqrt(n())) %>%
  ungroup()

@@

# Create the ggplot
promis_with_post_op_mental_vs_physical <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, color = health_variable)) +
  geom_line(size = 1.2) +
  scale_x_continuous(breaks = c(0, 1, 2)) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_errorbar(aes(ymin = mean_promis_score - sem_promis_score, ymax = mean_promis_score + sem_promis_score), width = 0.2, size = 0.8)  +
  theme(
       # plot.title = element_text(size=16, hjust = 0.55),
      #  axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
      #  axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
      #  legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white")) +
  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
       title = "PROMIS Scores by Anxiety Dose") +
#  scale_color_brewer(palette = "Set3") 
  scale_color_manual(values = custom_colors_simple)
promis_with_post_op_mental_vs_physical

# Create the ggplot -> bar
promis_with_post_op_mental_vs_physical_bar <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, fill = health_variable)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +  
  geom_errorbar(aes(ymin = mean_promis_score - sem_promis_score, ymax = mean_promis_score + sem_promis_score), 
                width = 0.2, size = 0.8, color = "black", position = position_dodge(width = 0.9)) +
  scale_x_continuous(breaks = c(0, 1, 2)) +
  scale_y_continuous(limits = c(0, 7)) +
  theme_minimal() +
  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
       title = "PROMIS Scores by Anxiety Dose") +
  scale_fill_manual(values = custom_colors)
